%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
{\Huge \scshape Robinpreet Singh Chahal} \\ \vspace{1pt}
Patiala, Punjab \\ \vspace{1pt}
\small \raisebox{-0.1\height}\faPhone\ +91-7696547986 ~
\href{mailto:mantar.1911@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{mantar.1911@gmail.com}} ~
\href{https://www.linkedin.com/in/robinpreet-singh-chahal-353762331/}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}} ~
\href{https://github.com/RobinChahal0010}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}}
\vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{Chitkara University}{2024 -- 2028}
{Bachelor of Engineering (B.E.) in Computer Science Engineering}{CGPA: 8.42/10}

\resumeSubHeadingListEnd


%------RELEVANT COURSEWORK-------



%-----------EXPERIENCE-----------


%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{PulseMQ} $|$ \emph{Java, Multithreading, Concurrent Queues}}
{\href{https://github.com/RobinChahal0010/PulseMQ}{\underline{GitHub}}}
\resumeItemListStart
\resumeItem{Built a Kafka-inspired event streaming engine using producer-consumer architecture and asynchronous message processing.}
\resumeItem{Implemented topic-based messaging with concurrent event delivery across multiple consumers.}
\resumeItem{Designed thread-safe queue management and event dispatching for scalable communication.}
\resumeItemListEnd

\vspace{-10pt}

\resumeProjectHeading
{\textbf{Route Optimization Engine} $|$ \emph{Java, Graph Algorithms}}
{\href{https://github.com/RobinChahal0010/java-route-optimization-engine}{\underline{GitHub}}}
\resumeItemListStart
\resumeItem{Developed an intelligent route optimization system using Dijkstra's shortest path algorithm.}
\resumeItem{Modeled dynamic road networks as weighted graphs for efficient pathfinding.}
\resumeItem{Implemented route computation and network traversal for transportation scenarios.}
\resumeItemListEnd

\vspace{-10pt}

\resumeProjectHeading
{\textbf{RateLimitEngine} $|$ \emph{Java, Backend Systems}}
{\href{https://github.com/RobinChahal0010/RateLimitEngine-Java}{\underline{GitHub}}}
\resumeItemListStart
\resumeItem{Built an API rate limiter using the Sliding Window algorithm to control request throughput.}
\resumeItem{Simulated backend throttling systems used by large-scale web services.}
\resumeItem{Implemented request tracking and window-based enforcement mechanisms.}
\resumeItemListEnd

\vspace{-10pt}

\resumeProjectHeading
{\textbf{JSync Subscription Engine} $|$ \emph{Java, OOP, System Design}}
{\href{https://github.com/RobinChahal0010/JSync-Subscription-Engine}{\underline{GitHub}}}
\resumeItemListStart
\resumeItem{Developed a SaaS subscription and billing engine inspired by platforms such as Netflix and Spotify.}
\resumeItem{Implemented auto-renewals, billing cycles, discount handling, and payment workflows.}
\resumeItem{Designed extensible object-oriented architecture for subscription management.}
\resumeItemListEnd

\vspace{-10pt}

\resumeProjectHeading
{\textbf{AgriSense AI} $|$ \emph{Python, Flask, Machine Learning}}
{\href{https://github.com/RobinChahal0010/AgriSense-AI}{\underline{GitHub}}}
\resumeItemListStart
\resumeItem{Built a crop recommendation platform using soil parameters and weather conditions.}
\resumeItem{Integrated machine learning models for crop recommendation based on soil nutrients, rainfall, and environmental conditions.}
\resumeItem{Used historical mandi price data to support data-driven agricultural decisions.}
\resumeItemListEnd

\resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Java, MySQL, Python, C++} \\
     \textbf{Core Java}{: OOP, Collections Framework, Exception Handling, Multithreading, JDBC} \\
     \textbf{Database}{: MySQL} \\
     \textbf{Computer Science Fundamentals}{: Data Structures and Algorithms, DBMS, Operating Systems, Computer Networks} \\
     \textbf{Tools}{: Git, GitHub, VS Code, Flask} \\
    }}
 \end{itemize}

%-----------INVOLVEMENT---------------
\section{Certifications}

\begin{itemize}
\item Oracle Cloud Infrastructure 2025 AI Foundations Associate (1Z0-1122-25)
\item Microsoft Certified: Azure AI Fundamentals (AI-900)
\item Microsoft Certified: Azure Fundamentals (AZ-900)
\item Microsoft Certified: Azure Data Fundamentals (DP-900)
\item Statistics Foundations -- Meta
\item Harness Git and GitHub -- Open Source Chandigarh
\end{itemize}



\end{document}
